% YAAC Another Awesome CV LaTeX Template
%
% Section: Experience
\sectionTitle{Experience}{\faSuitcase}
\begin{experiences}
\experience
{Current}{Lead Software Engineer / Architect}{SAGEL AI}{Aachen, Germany}{Feb 2024}
{
  \begin{itemize}
    \item Lead the full-stack design of Sagel AI’s conversational platform (Angular/React front ends, Node.js/Python microservices, PostgreSQL) using domain-driven modeling to keep APIs and services consistent.
    \item Build and deploy text/audio agents across WhatsApp, Email, Telegram, and bespoke telephony flows powered by Asterisk (VoIP/SIP, ARI, IVR), orchestrating OpenAI Realtime and Chat Completion APIs and validating integrations with Postman/Newman suites.
    \item Manage and mentor a four-person engineering squad across frontend, platform, telephony, and QA workstreams.
    \item Implement containerized infrastructure, CI/CD automation, ISO 42010-aligned architecture docs, GDPR-compliant data boundaries, and production monitoring while steering customer onboarding, sales, and delivery.
  \end{itemize}
}
{Angular,Node.js,Python,PostgreSQL,Asterisk,VoIP,CI/CD,AI}
\emptySeparator

\experience
{Feb 2024}{Embedded Systems Engineer}{Scharco Elektronik GmbH}{Wuppertal, Germany}{Oct 2022}
{
  \begin{itemize}
    \item Developed ESP32/STM32 firmware in ESP-IDF/CMake and integrated smart modules with the company cloud platform.
    \item Delivered Angular UI features and REST APIs surfacing embedded capabilities and telemetry to customers and service teams.
    \item Implemented ModBus, CAN, USB, Ethernet stacks, maintained GitHub-driven workflows, and authored ISO 42010-style interface contracts for production deployments.
  \end{itemize}
}
{ESP32,STM32,Embedded C++,Angular,ModBus,CAN,Cloud}
\emptySeparator

\experience
{Feb 2024}{Embedded Hardware Engineer}{Space Team Aachen e.V.}{Aachen, Germany}{Jan 2022}
{
  \begin{itemize}
    \item Designed redundant power electronics, fuse detection, and parachute release circuitry for the STAHR rocket program.
    \item Modeled STM32F4/CAN subsystems with KiCAD/LTSpice, including converters, LDOs, and protection topologies.
  \end{itemize}
}
{KiCAD,LTSpice,STM32F4,CAN,Power Electronics}
\emptySeparator

\experience
{Oct 2022}{Hardware / Software Developer}{Fraunhofer IPT}{Aachen, Germany}{Mar 2020}
{
  \begin{itemize}
    \item Engineered embedded devices for production lines, from PCB design (2--4 layers) to mechanical enclosures in Fusion 360/SolidWorks.
    \item Programmed STM32/ESP32 firmware, IoT stacks (HTTP/MQTT), and Python/Jupyter analytics for manufacturing data.
  \end{itemize}
}
{Embedded C++,Python,PCB Design,IoT,Firmware}
\emptySeparator
\end{experiences}
